\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}

### 2023-01-30 latex/supplementary.tex
added proofs for symmetric games 2 strategies

\theoremstyle{plainCl2}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{Cor}{Corollary}

@@

\begin{theorem}
When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of the introspection dynamics for the N-player additive game is given by: 
\begin{equation}
\ubf_a = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\label{Eq:additive-game-stationary-distribution}
\end{equation}
where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$.
\label{Th:additive-games-stationary-dist}
\end{theorem}
\noindent The above theorem gives a closed form expression of the stationary distribution of the introspection dynamics for additive multiplayer games. For any finite value of the selection parameter, $\beta$, the stationary distribution can be analytically calculated using the expression in Eq. (\ref{Eq:additive-game-stationary-distribution}). The expression is derived by assuming that the update process of the introspection dynamics is governed by Eq. (\ref{Eq:introspection-update}) and (\ref{Eq:introspection-normalization}). For proof, see Appendix \ref{Section:Appendix}.

\begin{theorem}
Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of the introspection dynamics with finite $\beta$ for the N-player additive game. Then, $\ubf_\abf$ is the product of the marginal probabilities that each player plays their respective actions in $\abf$. That is,

@@

\begin{equation}
\xi^j_{\abf_j} = \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\label{Eq:marginal-at-additive-game}
\end{equation}
\noindent where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$ in an additive game.
\label{Th:additive-game-product-of-marginals}
\end{theorem}

@@

\begin{equation}
\pi^i(\abf^i = \D, \abf^{-i}) - \pi^i(\abf^i = \C, \abf^{-i}) = c^i \left(1 - \frac{r^i}{N} \right) =: f(c^i, r^i) 
\label{Eq:difference-payoffs-lpgg}
\end{equation}
\\
\noindent is independent of $\abf^{-i}$. The linear public goods game is therefore an example of an additive game. This property of the game results in dominated strategies for player $i$ depending on the relationship between their productivity $r^i$ and number of players $N$. When $r^i < N$, the action of not contributing ($\D$) dominates the action of contributing ($\C$) and vice-versa. 
\\
\begin{lemma}
\label{prop:stationary-dist-lpgg}
When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for an asymmetric linear public goods game under introspection dynamics is given by: 
\\
\begin{equation}
\ubf_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^j)\beta f(c^j, r^j )}} \quad ,\forall \abf \in \{\C, \D\}^N
\label{Eq:stationary_dist_lpgg}
\end{equation}
where, 
\begin{equation}
\label{Eq:sign-function}
\mathit{sign}(a) =
\begin{cases}
1& \quad \text{if} \quad a = \C \\
-1& \quad \text{if} \quad a = \D
\end{cases}
\end{equation}
\end{lemma}

@@

\noindent In addition, when there are only two actions in the action set of players we define the action set in the same way as we did in the section of linear public goods game: $\mathcal{A} := \{\C, \D\}$. Since all players are symmetric in the two-action game, the number of states of the game can be reduced from  $2^N$ to $N+1$. Now, the state $k$ corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$. For the sake of notational simplicity, we denote the payoffs of a $\C$ and $\D$ player in the state $k$ as $\pi^{\C}(k)$ and $\pi^{\D}(k)$ respectively.

%We define following mapping function:  
%
%\begin{equation}
%e(a^i):= 
%\begin{cases}
%1 \quad \text{if} \quad a^i = a_\C \\
%0 \quad \text{if} \quad a^i = a_\D  
%\end{cases}
%\end{equation}
%\\
%We define $N_\C(\abf)$ as the number of $\C$ players in a state $\abf$. That is, 
%
%\begin{equation}
%N_\C(\abf) := \sum_{i = 1}^N e(\abf^i)
%\end{equation}
%\noindent 
%\\
\begin{lemma}
When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{a_\C, a_\D \}$, is given by:
\begin{equation}
\label{Eq:stationary-dist-symm-2-stgs}
\ubf_k = \frac{1}{T(k)} \cdot {N \choose k} \cdot \displaystyle \prod_{j=0}^{k} \displaystyle e^{\beta f(j-1)}
\end{equation}
where, $f(j) := \pi^\D(k+1) - \pi^\C(k)$ and $T(k)$ is the normalization factor, given by,
\begin{equation}
\label{Eq:normalization-Tk}
T(k) = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=0}^{k} \displaystyle e^{\beta f(j-1)}
\end{equation}
\end{lemma}

\section*{Appendix: Proofs}
\label{Section:Appendix}
\begin{proof}
\textbf{Proof of Theorem} \ref{Th:additive-games-stationary-dist} \\ \\ 
Since $\beta$ is finite, the transition matrix of the process $\T$ given by Eq. \ref{Eq:transition-matrix} is primitive and therefore, the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the row-stochastic transition matrix is unique and satisfies the conditions laid out in Eq. \ref{Eq:lefteigenvector} and \ref{Eq:normalizationcondition}. To continue for the rest of the proof, we introduce some short-cut notation that will be of use later in the proof:\\
\begin{align}
I_{q} &:= I(\abf_q,\abf), \quad \mathit{iff} \quad \abf_q \in \mathit{Neb}(\abf) \\ \notag \\ 
\label{Eq:shortcut-tau}
\tau^j_{\abf^j} &:= \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\end{align}
\noindent In order to show that the candidate stationary distribution, as proposed in Eq. \ref{Eq:additive-game-stationary-distribution} is the stationary distribution of the process, we need to show that the following are true:
\begin{eqnarray}
\label{step-one}
\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \ubf_a \quad \forall \abf \in \A \\ 
\label{step-two}
\sum_{\abf \in \A} \ubf_\abf  = 1
\end{eqnarray}
The Eq \ref{step-one} can be simplified further with the steps: 
\begin{align}
&\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \\
& \left( 1 - \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \ubf_{\abf} \right) + \sum_{\abf_q \in \mathit{Neb}(\abf)}  \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \ubf_{\abf_q} = \\ \notag \\
\label{eq:important-step}
& \ubf_\abf +  \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \left( \prod_{k \neq I_q} \tau^k_{\abf^k} \right) \left( p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} \right) \cdot \left(  \frac{1}{m^{I_q}-1} \right)
\end{align}
\\ Using the definition of probability of update of the introspection dynamics, as given by Eq. \ref{Eq:introspection-update} and Eq. \ref{Eq:shortcut-tau}, it can be shown that: 
\begin{equation}
p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} = 0
\label{important-step-is-zero}
\end{equation}
\\ \noindent Plugging the equality in Eq. \ref{important-step-is-zero} into Eq. \ref{eq:important-step}, we can see that the left hand side of Eq. \ref{step-one} indeed simplifies to $\ubf_{\abf}$. Now, to confirm that the candidate $\ubf$ is the unique stationary distribution we need to check if Eq. \ref{step-two} holds. Simplifying the left hand side of this equation shows that:
\begin{align}
\sum_{\abf \in \A} \ubf_\abf &= \sum_{\abf \in \A} \prod_{k=1}^N \tau^k_{\abf^k} \\ \notag \\
\label{step-prod-sum-sum-prod}
&= \left( \prod_{k=1}^N \sum_{\abf' \in \A} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\abf \in \A} \prod_{k=1}^N \displaystyle e^{\beta \pi^k_{\abf^k}} \right) \\ \notag \\
\label{step-prod-is-one}
&= 1
\end{align}
\noindent The step from Eq. \ref{step-prod-sum-sum-prod} to Eq \ref{step-prod-is-one} is possible because the sum and product in Eq. \ref{step-prod-sum-sum-prod} are interchangeable for both the terms. Therefore, condition Eq. \ref{step-two} is satisfied too. 
\end{proof}

\begin{proof}
\textbf{Proof of Theorem} \ref{Th:additive-game-product-of-marginals} \\ \\ 
If $\ubf$ is the unique stationary distribution of the $N-$player additive game with under the finite selection introspection dynamics, it is given by the expression in Eq. \ref{Eq:additive-game-stationary-distribution}. We calculate the marginal distribution of any arbitrary state $\abf$, $\xi_{\abf} = (\xi^j_{\abf^j})_{j = 1,2,...,N}$ by using the definition of marginal distribution in Eq. \ref{Eq:marginal-definition}. It follows that: 
\begin{align}
\xi^j_{\abf^j} &= \sum_{\mathbf{b} \in \A^{-j}} \ubf_{(\abf^j,\mathbf{b})} \\ \notag \\
&= \left( \prod_{k=1}^N \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \prod_{k\neq j} \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\ 
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\abf' \in \A^{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\ 
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \left( \pi^j_{\abf'} - \pi^j_{\abf^j}\right)}\right)^{-1}
\end{align}
\noindent Therefore, the marginal distribution follows Eq.  \ref{Eq:marginal-at-additive-game}. Now since we also additionally know that the stationary distribution follows the form Eq. \ref{Eq:additive-game-stationary-distribution}, we can conclude that for additive games, under introspection dynamics with finite selection, Eq. \ref{Eq:additive-game-products} holds. 
\end{proof}

@@

\textbf{Proof of lemma} \ref{prop:stationary-dist-lpgg} \\ \\

@@

&\bar{\abf}^j := \{a_\D,a_\C\} \setminus \abf^j  \\ 
&p^j := \frac{1}{1 + \displaystyle e^{\beta f(c^j, r^j)}}

@@

Using these notations and Eq. \ref{Eq:introspection-update} and \ref{Eq:difference-payoffs-lpgg} we can write the probability that a player $j$ updates from $\abf^j$ to $\bar{\abf}^j$ while their co-players play $\abf^{-j}$ as:

@@

p^j_{\displaystyle \bar{\abf}^j  \to \abf^j} (\abf^{-j}) = p^j \mathit{sign}(\abf^j) + \bar{\abf}^j \\ \\

@@

\ubf_\abf = \prod_{k = 1}^{N}  p^k \mathit{sign}(\abf^k) + \bar{\abf}^k \quad ,\forall \abf \in \{0,1\}^N

@@

&\ubf_\abf = \T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}  \\ 

@@

&\sum_{\forall \abf_q} u_{\abf_q}= 1

@@

\T_{\abf,\abf} = 1 - \sum_{k=1}^{N} \T_{(\abf^k, \abf^{-k}), (\bar{\abf}^k,\abf^{-k})} = 1 - \frac{1}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \abf^k 

@@

\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \sum_{k = 1}^N \T_{(\bar{\abf}^k,\abf^{-k}), (\abf^k, \abf^{-k})} \ubf_{(\bar{\abf}^k,\abf^{-k})} \\
&= \frac{1}{N} \sum_{k = 1}^N \left(p^k \textit{sign}(\abf^k) + \bar{\abf}^k \right) \ubf_{(\bar{\abf}^k,\abf^{-k})} \\ 

@@

&= \frac{\ubf_\abf}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \abf^k 

@@

\sum_{\forall \abf_q} u_{\abf_q} =& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^N p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k \\
=& \displaystyle \displaystyle \sum_{\forall \abf_q} (1-p^N)  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k  + p^N  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k \\ 
=& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k

@@

\section*{Supplementary References}
\bibliographystyle{unsrt}
\bibliography{bibliography.bib }
\end{document}

>>>>

\theoremstyle{plainCl2}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{Corollary}{Corollary}

@@

\begin{Prop}
When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of the introspection dynamics for the N-player additive game is given by: 
\begin{equation}
\ubf_a = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\label{Eq:additive-game-stationary-distribution}
\end{equation}
where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$.
\label{Th:additive-games-stationary-dist}
\end{Prop}
\noindent The above theorem gives a closed form expression of the stationary distribution of the introspection dynamics for additive multiplayer games. For any finite value of the selection parameter, $\beta$, the stationary distribution can be analytically calculated using the expression in Eq. (\ref{Eq:additive-game-stationary-distribution}). The expression is derived by assuming that the update process of the introspection dynamics is governed by Eq. (\ref{Eq:introspection-update}) and (\ref{Eq:introspection-normalization}). For proof, see Appendix \ref{Section:Appendix}.

\begin{Prop}
Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of the introspection dynamics with finite $\beta$ for the N-player additive game. Then, $\ubf_\abf$ is the product of the marginal probabilities that each player plays their respective actions in $\abf$. That is,

@@

\begin{equation}
\xi^j_{\abf_j} = \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\label{Eq:marginal-at-additive-game}
\end{equation}
\noindent where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$ in an additive game.
\label{Th:additive-game-product-of-marginals}
\end{Prop}

@@

\begin{equation}
\pi^i(\abf^i = \D, \abf^{-i}) - \pi^i(\abf^i = \C, \abf^{-i}) = c^i \left(1 - \frac{r^i}{N} \right) =: f(c^i, r^i) 
\label{Eq:difference-payoffs-lpgg}
\end{equation}
\\
\noindent is independent of $\abf^{-i}$. The linear public goods game is therefore an example of an additive game. This property of the game results in dominated strategies for player $i$ depending on the relationship between their productivity $r^i$ and number of players $N$. When $r^i < N$, the action of not contributing ($\D$) dominates the action of contributing ($\C$) and vice-versa. 
\\
\begin{Prop}
\label{prop:stationary-dist-lpgg}
When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for an asymmetric linear public goods game under introspection dynamics is given by: 
\\
\begin{equation}
\ubf_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^j)\beta f(c^j, r^j )}} \quad ,\forall \abf \in \{\C, \D\}^N
\label{Eq:stationary_dist_lpgg}
\end{equation}
where, 
\begin{equation}
\label{Eq:sign-function}
\mathit{sign}(a) =
\begin{cases}
1& \quad \text{if} \quad a = \C \\
-1& \quad \text{if} \quad a = \D
\end{cases}
\end{equation}
\end{Prop}

@@

\noindent In addition, when there are only two actions in the action set of players we define the action set in the same way as we did in the section of linear public goods game: $\mathcal{A} := \{\C, \D\}$. 
\subsection*{Notations}
We introduce some notations before presenting the results
\begin{enumerate}

\item We denote the payoffs of a $\C$ and $\D$ player when they have $j$ co-players playing $\C$, as $\pi^{\C}(j)$ and $\pi^{\D}(j)$ respectively. 
\item We define a simple mapping function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to $0$. That is, 
\begin{equation}
\alpha(a):= 
\begin{cases}
1 \quad \text{if} \quad a = \C \\
0 \quad \text{if} \quad a = \D  
\end{cases}
\end{equation}
\item For every state $\abf \in \mathcal{A}^N$, we count the number of $\C$ players in the state and denote it with $\mathcal{C}(\abf)$. That is, 
\begin{equation}
\mathcal{C}(\abf) := \sum_{j=1}^N \alpha(\abf^j)
\end{equation}
\end{enumerate}
\newpage
\begin{Prop}
\label{Prop:Symmetric-2-strategies-state}
When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, $(\ubf_{\abf})_{\abf \in \mathcal{A}^N}$, is given by:
\begin{equation}
\label{Eq:stationary-dist-symm-2-stgs-state}
\ubf_\abf = \frac{1}{\Gamma} \displaystyle \prod_{j=1}^{\mathcal{C}(\abf)} \displaystyle e^{-\beta f(j-1)}
\end{equation}
where $f(j) := \pi^\D(j) - \pi^\C(j)$ is the difference in payoffs of playing $\D$ and $\C$ when there are $j$ co-players playing $\C$. The term $\Gamma$ is the normalization factor given by:
\begin{equation}
\label{Eq:stationary-dist-normalization-symm-2-stgs-state}
\Gamma = \displaystyle \sum_{\forall \abf' \in \mathcal{A}^N} \prod_{j = 1}^{\mathcal{C}(\abf')} \displaystyle e^{-\beta f(j-1)}
\end{equation}
\end{Prop}

\noindent The above proposition gives an exact closed form expression for the steady state distribution of the introspection dynamics for symmetric games with two strategies. Since all players are symmetric in this two strategy game, the number of unique states of the game can be reduced to $N+1$ from $2^N$. Now, the state $k$ corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$. Then, Proposition \ref{Prop:Symmetric-2-strategies-state} can be simplified by accounting for states with number of $\C$ players as follows:

\begin{Corollary}
\label{Lemma: Symmetric-2-stg}
When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, is given by \\
\label{Eq:stationary-dist-symm-2-stgs}
\ubf_k = \frac{1}{\Gamma} \cdot {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}
\end{equation} \\ 
where, $k$ represents the number of $\C$ players in the state and $f(j) := \pi^\D(j) - \pi^\C(j)$ is the difference in payoffs of playing $\D$ and $\C$ when there are $j$ co-players playing $\C$. The term $\Gamma$ is the normalization factor, given by, \\
\label{Eq:normalization-Tk}
\Gamma = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=1}^{k+1  } \displaystyle e^{-\beta f(j-1)}
\end{Corollary}
\noindent The above lemma follows directly from Proposition \ref{Prop:Symmetric-2-strategies-state}. The key step is to count the number of states in the state space $\mathcal{A}^N$ that corresponds to exactly $k$, $\C$ players and $N-k$, $\D$ players. This count is simply the binomal coefficient $N \choose k$. For details see the proof in the Appendix. 
\newpage 
\section*{Appendix: Proofs}
\label{Section:Appendix}

@@

\textbf{Proof of Proposition} \ref{Th:additive-games-stationary-dist} \\ \\ 
Since $\beta$ is finite, the transition matrix of the process $\T$ given by Eq. \ref{Eq:transition-matrix} is primitive and therefore, the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the row-stochastic transition matrix is unique and satisfies the conditions laid out in Eq. \ref{Eq:lefteigenvector} and \ref{Eq:normalizationcondition}. To continue for the rest of the proof, we introduce some short-cut notation that will be of use later in the proof:\\
I_{q} &:= I(\abf_q,\abf), \quad \mathit{iff} \quad \abf_q \in \mathit{Neb}(\abf) \\ \notag \\ 
\label{Eq:shortcut-tau}
\tau^j_{\abf^j} &:= \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\noindent In order to show that the candidate stationary distribution, as proposed in Eq. \ref{Eq:additive-game-stationary-distribution} is the stationary distribution of the process, we need to show that the following are true:
\label{step-one}
\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \ubf_a \quad \forall \abf \in \A \\ 
\label{step-two}
\sum_{\abf \in \A} \ubf_\abf  = 1
The Eq \ref{step-one} can be simplified further with the steps: 
&\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \\
& \left( 1 - \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \ubf_{\abf} \right) + \sum_{\abf_q \in \mathit{Neb}(\abf)}  \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \ubf_{\abf_q} = \\ \notag \\
\label{eq:important-step}
& \ubf_\abf +  \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \left( \prod_{k \neq I_q} \tau^k_{\abf^k} \right) \left( p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} \right) \cdot \left(  \frac{1}{m^{I_q}-1} \right)
\\ Using the definition of probability of update of the introspection dynamics, as given by Eq. \ref{Eq:introspection-update} and Eq. \ref{Eq:shortcut-tau}, it can be shown that: 
p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} = 0
\label{important-step-is-zero}
\\ \noindent Plugging the equality in Eq. \ref{important-step-is-zero} into Eq. \ref{eq:important-step}, we can see that the left hand side of Eq. \ref{step-one} indeed simplifies to $\ubf_{\abf}$. Now, to confirm that the candidate $\ubf$ is the unique stationary distribution we need to check if Eq. \ref{step-two} holds. Simplifying the left hand side of this equation shows that:
\sum_{\abf \in \A} \ubf_\abf &= \sum_{\abf \in \A} \prod_{k=1}^N \tau^k_{\abf^k} \\ \notag \\
\label{step-prod-sum-sum-prod}
&= \left( \prod_{k=1}^N \sum_{\abf' \in \A} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\abf \in \A} \prod_{k=1}^N \displaystyle e^{\beta \pi^k_{\abf^k}} \right) \\ \notag \\
\label{step-prod-is-one}
&= 1
\noindent The step from Eq. \ref{step-prod-sum-sum-prod} to Eq. \ref{step-prod-is-one} is possible because the sum and product in Eq. \ref{step-prod-sum-sum-prod} are interchangeable for both the terms. Therefore, condition Eq. \ref{step-two} is satisfied too. 

\begin{proof}
\textbf{Proof of Proposition} \ref{Th:additive-game-product-of-marginals} \\ \\ 
If $\ubf$ is the unique stationary distribution of the $N-$player additive game with under the finite selection introspection dynamics, it is given by the expression in Eq. \ref{Eq:additive-game-stationary-distribution}. We calculate the marginal distribution of any arbitrary state $\abf$, $\xi_{\abf} = (\xi^j_{\abf^j})_{j = 1,2,...,N}$ by using the definition of marginal distribution in Eq. \ref{Eq:marginal-definition}. It follows that: 
\begin{align}
\xi^j_{\abf^j} &= \sum_{\mathbf{b} \in \A^{-j}} \ubf_{(\abf^j,\mathbf{b})} \\ \notag \\
&= \left( \prod_{k=1}^N \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \prod_{k\neq j} \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\ 
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\abf' \in \A^{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\ 
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \left( \pi^j_{\abf'} - \pi^j_{\abf^j}\right)}\right)^{-1}
\end{align}
\noindent Therefore, the marginal distribution follows Eq.  \ref{Eq:marginal-at-additive-game}. Now since we also additionally know that the stationary distribution follows the form Eq. \ref{Eq:additive-game-stationary-distribution}, we can conclude that for additive games, under introspection dynamics with finite selection, Eq. \ref{Eq:additive-game-products} holds. 
\end{proof}
\textbf{Proof of Proposition} \ref{prop:stationary-dist-lpgg} \\ \\

@@

\bar{\abf}^j &:= \{\D,\C\} \setminus \abf^j  \\ 
p^j &:= \frac{1}{1 + \displaystyle e^{\beta f(c^j, r^j)}} 

@@

In addition we introduce a mapping function $\alpha(.)$ which maps the action $\C$ to 1 and the action $\D$ to 0. That is $\alpha(\C) := 1$ and $\alpha(\D) := 0$. Using these notations and Eq. \ref{Eq:introspection-update} and \ref{Eq:difference-payoffs-lpgg} we can write the probability that a player $j$ updates from $\abf^j$ to $\bar{\abf}^j$ while their co-players play $\abf^{-j}$ as: \\

@@

p^j_{\displaystyle \bar{\abf}^j  \to \abf^j} (\abf^{-j}) = p^j \mathit{sign}(\abf^j) + \alpha(\bar{\abf}^j) \\ \\

@@

\ubf_\abf = \prod_{k = 1}^{N}  p^k \mathit{sign}(\abf^k) + \alpha(\bar{\abf}^k) \quad ,\forall \abf \in \{0,1\}^N

@@

&\ubf_\abf = \T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}  \\[10pt] 

@@

&\sum_{\forall \abf_q} \ubf_{\abf_q}= 1

@@

\T_{\abf,\abf} = 1 - \sum_{k=1}^{N} \T_{(\abf^k, \abf^{-k}), (\bar{\abf}^k,\abf^{-k})} = 1 - \frac{1}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \alpha(\abf^k)

@@

\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \sum_{k = 1}^N \T_{(\bar{\abf}^k,\abf^{-k}), (\abf^k, \abf^{-k})} \ubf_{(\bar{\abf}^k,\abf^{-k})} \\[10pt]
&= \frac{1}{N} \sum_{k = 1}^N \left(p^k \textit{sign}(\abf^k) +\alpha(\bar{\abf}^k) \right) \ubf_{(\bar{\abf}^k,\abf^{-k})} \\[10pt] 

@@

&= \frac{\ubf_\abf}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \alpha(\abf^k) 

@@

\sum_{\forall \abf_q} u_{\abf_q} =& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^N p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k) \\[10pt]
=& \displaystyle \displaystyle \sum_{\forall \abf_q} (1-p^N)  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k)  + p^N  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k) \\[10pt]
=& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k)

@@

\textbf{Proof of Proposition} \ref{Prop:Symmetric-2-strategies-state} \\ \\
By construction, the candidate stationary distribution given by Eq. \ref{Eq:stationary-dist-symm-2-stgs-state} and Eq. \ref{Eq:stationary-dist-normalization-symm-2-stgs-state} is a probability distribution since it satisfies the condition in Eq. \ref{Eq:normalizationcondition} and for any state $\abf'$, $\ubf_{\abf'}$ is between 0 and 1.  Moreover, since $\beta$ is finite, the transition matrix of the process $\T$ is primitive and therefore, it will have a unique stationary distribution. To show that the candidate stationary distribution is the unique stationary distribution, we need to check if for this process, $\ubf \T= \ubf$. That is, the Eq. \ref{Eq:transition-in-proof} must hold. We re-introduce some notations that we will use in this proof: 
\bar{\abf}^j &:= \{\D,\C\} \setminus \abf^j \\[10pt]
\alpha(a)&:= 
\begin{cases}
1 \quad \text{if} \quad a = \C \\[10pt]
0 \quad \text{if} \quad a = \D 
\end{cases}\\[10pt]
\mathcal{C}(\abf) &= \sum_{j=1}^N \alpha(\abf^j)
